Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-27 xrb2/paper.tex
fix accretion rate stuff so it's more agnostic on the high vs low accretion rate causing increased crustal heating front

The temperature structure of the accreted fuel layer can also affect
the flame propagation.  \citet{Timmes00} showed that laminar helium flames 
have higher speeds when moving into hotter upstream fuel.
It is known that crustal heating is stronger at lower
accretion rates and weaker at higher accretion rates, due to the
effect of neutrino losses \citep{Cumming2006,johnston:2019}. 
A shallow heating
mechanism of as yet unknown origin has been found necessary to
reproduce observed properties of XRBs in 1D simulations
\citep{Deibel2015,Turlione2015,Keek2017}.
In our
models, we keep the crust at a constant temperature, so by increasing
this temperature we can effectively increase the crustal heating, shallow heating
and/or
mimic the effects of lower accretion rates.

@@

To explore the effect of different initial temperature configurations, we run four simulations fixed at a rotation rate of $500~\mathrm{Hz}$ with temperatures as shown in Table~\ref{table:runs}. For all the $500~\mathrm{Hz}$ simulations (with the exception of the coolest run, $\tt{F500}$), we set $T_\mathrm{star}$ = $T_\mathrm{hi}$, scaling $\delta T$ accordingly to maintain a consistent value of $T_\mathrm{hi} + \delta T$. If we let $T_\mathrm{star} < T_\mathrm{hi}$, the cooler neutron star surface might act as a heat sink and siphon away energy that would otherwise go into heating the burning layer. By choosing $T_\mathrm{star}$ = $T_\mathrm{hi}$, we can effectively explore simulations with greater surface heating. There are several physically distinct mechanisms that could produce an increased temperature at the crust: crustal heating, some other form of shallow heating or a higher accretion rate. In these simulations, we do not model the mechanism producing the heating effect, just the effect itself, so we do not distinguish between which of these mechanisms cause the heating.

>>>>

The temperature structure of the accreted fuel layer can also affect
the flame propagation.  \citet{Timmes00} showed that laminar helium flames 
have higher speeds when moving into hotter upstream fuel.
It has been suggested that crustal heating may be stronger at lower
accretion rates and weaker at higher accretion rates, due to the
effect of neutrino losses \citep{Cumming2006,johnston:2019}, however at 
very high accretion rates it has been observed that the entire atmosphere 
simmers in place rather than a flame propagating across the surface \citep{fujimoto1981,bildsten1998thermonuclear,keek2009effect}. 
A shallow heating
mechanism of as yet unknown origin has been found necessary to
reproduce observed properties of XRBs in 1D simulations
\citep{Deibel2015,Turlione2015,Keek2017}.
In our
models, we keep the crust at a constant temperature, so by increasing
this temperature we can effectively increase the crustal heating, shallow heating
and/or
mimic the effects of accretion-induced heating.

@@

To explore the effect of different initial temperature configurations, we run four simulations fixed at a rotation rate of $500~\mathrm{Hz}$ with temperatures as shown in Table~\ref{table:runs}. For all the $500~\mathrm{Hz}$ simulations (with the exception of the coolest run, $\tt{F500}$), we set $T_\mathrm{star}$ = $T_\mathrm{hi}$, scaling $\delta T$ accordingly to maintain a consistent value of $T_\mathrm{hi} + \delta T$. If we let $T_\mathrm{star} < T_\mathrm{hi}$, the cooler neutron star surface might act as a heat sink and siphon away energy that would otherwise go into heating the burning layer. By choosing $T_\mathrm{star}$ = $T_\mathrm{hi}$, we can effectively explore simulations with greater surface heating. There are several physically distinct mechanisms that could produce an increased temperature at the crust: crustal heating, some other form of shallow heating or accretion-induced heating. In these simulations, we do not model the mechanism producing the heating effect, just the effect itself, so we do not distinguish between which of these mechanisms cause the heating.
